---
title: "Model Distillation: Liver SOFA Example"
author: 
  - anonymous
  
date: '`r format(Sys.Date(), "%B %d, %Y")`'

output:
  pdf_document:
    latex_engine: xelatex
  bookdown::pdf_book: default
    
urlcolor: blue
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      cache.lazy = FALSE,
                      dev = c("png"),
                      dpi = 300,
                      fig.path = 'figures/',
                      fig.keep = "high")

#added from: https://github.com/yihui/knitr-examples/blob/master/077-wrap-output.Rmd
library(knitr)
hook_output = knit_hooks$get('output')
knit_hooks$set(output = function(x, options) {
  # this hook is used only when the linewidth option is not NULL
  if (!is.null(n <- options$linewidth)) {
    x = knitr:::split_lines(x)
    # any lines wider than n should be wrapped
    if (any(nchar(x) > n)) x = strwrap(x, width = n)
    x = paste(x, collapse = '\n')
  }
  hook_output(x, options)
})

```




```{r, message=FALSE}
library(tidyverse) # A collection of packages for data science. More about it on 
                   # www.tidyverse.com
library(magrittr)  # A package that provides pipe operators like %>%
library(mgcv)      # A package written by Simon Wood that implements his 
                   # (spline based) GAM specification.
library(glue)      # A package that provides interpolated string functions.
```


```{r function: powerSet, include=FALSE}
#When you want to reproduce the examples, you have to run this code chunk in advance!!
powerSet <- function(set) {
  
    apply(X      = rep(list(c(T,F)), length = length(set)) %>% expand.grid(.),
          MARGIN = 1,
          FUN    = function(...) set[...])
}
```



```{r function: Accuracy Measures for multiclass, include=FALSE}
accuracy <- 
  function(y, y_hat, filter = TRUE) mean((y == y_hat)[filter])

class_accuracy <-
  function(y, y_hat, classes = sort(unique(y))) 
    sapply(as.character(classes), function(c) accuracy(y, y_hat, filter = (y == as.numeric(c))))
```


```{r read data sets, include=FALSE}
train_data <- readRDS("train_set_with_sofa_predictions.rds")

test_data <- readRDS("test_set_with_sofa_predictions.rds")
```


Learner: Feed forward neural network with seven layers (number of neurons per 
layer: 128, 161, 203 , 256, 203 , 161, 128) and relu activation function. 
The network was trained with SGD (batch size 64) and learning rate .01 for 5 
epochs and a dropoutrate of .2 for inter hidden layer weights. All other 
optimizer settings are default values of pyTorch's SGD optimizer. The objective 
function was MSE. 

In a second step thresholds to turn the network output (score) 
into class predictions were learned . For this purpose a ordinal regression model 
was trained (R package "ordinal"). 

Train set size: `r nrow(train_data)` measurement points.
Test set size: `r nrow(test_data)` measurement points.


\newpage
## PERFORMANCE EVALUATION

### CIRCULAR MODEL - TRAIN SET ACCURACY (overall and per class) 

```{r accuracy measures on train set for circular teacher, echo=FALSE}
with(train_data, accuracy(target, sofa_circ))
with(train_data, class_accuracy(target, sofa_circ))
```

Confusion Matrix:
```{r, echo=FALSE}
xtabs(~ target + sofa_circ, data = train_data)
```


### CIRCULAR MODEL - TEST SET ACCURACY (overall and per class) 

```{r accuracy measures on test set for circular teacher, echo=FALSE}
acc_circ <- with(test_data, accuracy(target, sofa_circ))
print(acc_circ)
with(test_data, class_accuracy(target, sofa_circ))
```

Confusion Matrix:
```{r, echo=FALSE}
xtabs(~ target + sofa_circ, data = test_data)
```

\newpage
### NON-CIRCULAR MODEL - TRAIN SET ACCURACY (overall and per class) 

```{r accuracy measures on train set for non-circular teacher, echo=FALSE}
with(train_data, accuracy(target, sofa_nocirc))
with(train_data, class_accuracy(target, sofa_nocirc))
```

Confusion Matrix:
```{r, echo=FALSE}
xtabs(~ target + sofa_nocirc, data = train_data)
```


### NON-CIRCULAR MODEL - TEST SET ACCURACY (overall and per class) 

```{r accuracy measures on test set for non-circular teacher, echo=FALSE}
acc_nocirc <- with(test_data, accuracy(target, sofa_nocirc))
print(acc_nocirc)
with(test_data, class_accuracy(target, sofa_nocirc))
```

Confusion Matrix:
```{r, echo=FALSE}
xtabs(~ target + sofa_nocirc, data = test_data)
```





\newpage
### CORRELATION PATTERN
```{r load libraries to draw circular heatmap, include=FALSE}
library(circlize)
#to install package "ComplexHeatmap":
#install.packages("BiocManager")
#BiocManager::install("ComplexHeatmap")
library(ComplexHeatmap)
library(gridBase)
```


```{r calc correlations,include=FALSE}
method <- "pearson"

corr_matrix <-
  cbind(
    "Label"        = sapply(select(test_data, amv:horovitz), 
                            cor,
                            method = method,
                            y = test_data$target),
    "DNN w bili"     = sapply(select(test_data, amv:horovitz), 
                            cor,
                            method = method,
                            y = test_data$sofa_circ),
    "DNN wo bili" = sapply(select(test_data, amv:horovitz), 
                            cor,
                            method = method,
                            y = test_data$sofa_nocirc))
```



```{r liver_distill_fig1 , fig.height = 4.5, fig.width = 5.5, fig.align = "center", warning=FALSE, message=FALSE, echo=FALSE}

plot.new()
circle_size = unit(1, "snpc") # snpc unit gives you a square region

pushViewport(viewport(x = 0, 
                      y = 0.5, 
                      width = circle_size, 
                      height = circle_size, 
                      just = c("left", "center")))


col_scale <- 
  colorRamp2(c(-1, 0, 1), c("#67001F", "#FFFFFF", "#053061"), space ="LAB")

par(omi = gridOMI(), new = TRUE)
par(mar = c(0.1, 0.1, 0.1, 0.1))
circos.par(gap.after = 35, cell.padding = c(0, 0, 0, 0))


  circos.heatmap(corr_matrix[, 3, drop = FALSE], 
                 col = col_scale, 
                 track.height = .1,
                 rownames.side = "outside",
                 rownames.font = 2)
                 #rownames.cex = 0.5 + .25 * rownames(corr_matrix) %in% vars)
  circos.track(track.index = 2, 
               panel.fun = function(x, y) {
                  cn = colnames(corr_matrix)[3]
                  n  = length(cn)
                  circos.text(rep(CELL_META$cell.xlim[2], n) + convert_x(1, "mm"), 
                              1:n - 0.5, cn, 
                              cex = 0.75, 
                              adj = c(0, 0.5), 
                              facing = "bending.inside",
                              niceFacing = TRUE,
                              font = 2)},
              bg.border = NA)
  
                
  circos.heatmap(corr_matrix[,2 , drop = FALSE], 
               col = col_scale, 
               track.height = .1)
  circos.track(track.index = 3,
               panel.fun = function(x, y) {
                  cn = colnames(corr_matrix)[2]
                  n = length(cn)
                  circos.text(rep(CELL_META$cell.xlim[2], n) + convert_x(1, "mm"), 
                              1:n - 0.5, cn, 
                              cex = 0.75, 
                              adj = c(0, 0.5), 
                              facing = "bending.inside",
                              niceFacing = TRUE,
                              font = 2)},
              bg.border = NA)
  
  
  circos.heatmap(corr_matrix[,1 , drop = FALSE], 
               col = col_scale, 
               track.height = .1)
  circos.track(track.index = 4,
               panel.fun = function(x, y) {
                  cn = colnames(corr_matrix)[1]
                  n = length(cn)
                  circos.text(rep(CELL_META$cell.xlim[2], n) + convert_x(1, "mm"), 
                              1:n - 0.5, cn, 
                              cex = 0.75, 
                              adj = c(0, 0.5), 
                              facing = "bending.inside",
                              niceFacing = TRUE,
                              font = 2)},
              bg.border = NA)
  
  circos.clear()

upViewport()

lgd_color <- 
  Legend(at = seq(-1, 1, .2), 
         col_fun = col_scale, 
         title_position = "topcenter", 
         title = "r",
         border = "black")
draw(lgd_color,  x = circle_size, just = "left")
```


\newpage
## NULLIFICATION
```{r train student gams which have access to all features, warning=FALSE, cache=TRUE, include=FALSE}
#list_wo_bili <- 
#  paste0(c(glue("s({names(test_data)[-c(8, 42, 45:47)]})"), 
#           names(test_data)[42]),
#        collapse = " + ")

list_wo_bili <- 
  corr_matrix[order(abs(corr_matrix[,"DNN wo bili"]), decreasing=TRUE),][2:5,] %>%
  rownames(.) %>% 
  paste0("s(", .,")") %>%
  paste0(., collapse = " + ")

student_nocirc_all <- 
  gam(as.formula(paste0("sofa_nocirc ~ s(bili) + ", list_wo_bili)), 
      data = test_data)

student_circ_all <- 
  gam(as.formula(paste0("sofa_circ ~ s(bili, k=100) + ", list_wo_bili)), 
      data = test_data)
```



```{r train student gams which have access to non-circular features only, warning=FALSE, cache=TRUE, include=FALSE}
#list_wo_bili <- 
#  paste0(c(glue("s({names(test_data)[-c(8, 42, 45:47)]})"), 
#           names(test_data)[42]),
#        collapse = " + ")

list_wo_bili <- 
  corr_matrix[order(abs(corr_matrix[,"DNN wo bili"]), decreasing=TRUE),][2:5,] %>%
  rownames(.) %>% 
  paste0("s(", .,")") %>%
  paste0(., collapse = " + ")

student_nocirc_noBili <- 
  gam(as.formula(paste0("sofa_nocirc ~ ", list_wo_bili)), 
      data = test_data)

student_circ_noBili <- 
  gam(as.formula(paste0("sofa_circ ~ ",list_wo_bili)), 
      data = test_data)
```


<!-- ### TEACHER: circular, STUDENT: all features -->
```{r, echo=FALSE, include=FALSE}
summary(student_circ_all)
```

\newpage
<!-- ### TEACHER: circular, STUDENT: no bili -->
```{r, echo=FALSE, include=FALSE}
summary(student_circ_noBili)
```

\newpage
<!-- ### TEACHER: non-circular, STUDENT: all features -->
```{r,echo=FALSE, include=FALSE}
summary(student_nocirc_all)
```

\newpage
<!-- ### TEACHER: non-circular, STUDENT: no bili -->
```{r,echo=FALSE, include=FALSE}
summary(student_nocirc_noBili)
```

\newpage
```{r select 5 most important featurs for non-circ model based on corr, include=FALSE, eval=FALSE}
corr_matrix[order(abs(corr_matrix[,"circular"]), decreasing=TRUE),][1:5,]
```

```{r liver_distill_fig2, echo=FALSE, warning=FALSE, fig.height = 11.7, fig.width = 8.3, fig.align = "center"}
dev_nobili_circ <- round(summary(student_circ_noBili)$dev.expl * 100)
dev_all_circ <- round(summary(student_circ_all)$dev.expl * 100)

dev_nobili_nocirc   <- round(summary(student_nocirc_noBili)$dev.expl * 100)
dev_all_nocirc <- round(summary(student_nocirc_all)$dev.expl * 100)

jump_bili <- function(x) (x > 12) + (x > 6) + (x > 2) + (x > 1.2) + 0

par(mfrow = c(5,4),  mar=c(1,1,3,1), oma = c(1,1,2,1))



#first row: bilirubin 
 #non-circular model
   plot(x = 0:15, y = seq(0,4, length.out=16),
     xlim   = c(0,15), 
     ylim   = c(0,4),
     main   = glue("GAM w/o Bilirubin (D\U00B2={dev_nobili_nocirc}%)"),
     ylab   = "", 
     xlab   = "",
     #yaxt   = "n",
     type   = "n")
  text(labels = "not included in student GAM",
       x      = mean(c(0,15)),
       y      = mean(c(0,4)),
       adj    = .5)
  
  mtext(glue("Black-Box Model without Bilirubin (Acc.={floor(acc_nocirc * 100)}%)"), font = 2, side = 3, line = 0, outer = TRUE, at = .25)
  
  plot(student_nocirc_all, 
     se     = FALSE, 
     #rug   = TRUE, 
     xlim   = c(0,15), 
     ylim   = c(0,4),
     main   = glue("GAM w/ Bilirubin (D\U00B2={dev_all_nocirc}%)"),
     ylab   = "", 
     xlab   = "",
     yaxt   = "n", 
     select = 1)
   rug(unique(test_data$bili))
    curve(jump_bili, from = 0, to = 15, n = 1001, add = TRUE, col = "blue", lty="dashed")
   abline(v = c(1.2, 2, 6, 12), col = "blue", lty="dotted")
   curve(jump_bili, from = 0, to = 15, n = 1001, add = TRUE, col = "blue", lty="dashed")
   abline(v = c(1.2, 2, 6, 12), col = "blue", lty="dotted")
   legend(legend = c("Definition", "Learned"), 
          col    = c("blue", "black"),
          lty    = c("dashed", "solid"),
          bty    = "o",
          bg     = "white",
          x      = "topleft")

  
  
    #circular model
   plot(x = 0:15, y = seq(0,4, length.out=16),
     xlim   = c(0,15), 
     ylim   = c(0,4),
     main   = glue("GAM w/o Bilirubin (D\U00B2={dev_nobili_circ}%)"),
     ylab   = "", 
     xlab   = "",
     yaxt   = "n",
     type   = "n")
  text(labels = "not included in GAM",
       x      = mean(c(0,15)),
       y      = mean(c(0,4)),
       adj    = .5)
  
  mtext(glue("Black-Box Model with Bilirubin (Acc.={floor(acc_circ*100)}%)"), font = 2, side = 3, line = 0, outer = TRUE, at = .75)
  
  plot(student_circ_all, 
     se     = FALSE, 
     #rug   = TRUE, 
     xlim   = c(0,15), 
     ylim   = c(0,4),
     main   = glue("GAM w/ Bilirubin (D\U00B2={dev_all_circ}%)"),
     ylab   = "", 
     xlab   = "",
     yaxt   = "n", 
     #ann=FALSE,
     select = 1,
     shift  = coef(student_circ_all)[1])
   rug(unique(test_data$bili))
  curve(jump_bili, from = 0, to = 15, n = 1001, add = TRUE, col = "blue", lty="dashed")
   abline(v = c(1.2, 2, 6, 12), col = "blue", lty="dotted")
   curve(jump_bili, from = 0, to = 15, n = 1001, add = TRUE, col = "blue", lty="dashed")
   abline(v = c(1.2, 2, 6, 12), col = "blue", lty="dotted")
   legend(legend = c("Definition", "Learned"), 
          col    = c("blue", "black"),
          lty    = c("dashed", "solid"),
          bty    = "o",
          bg     = "white",
          x      = "topleft")
  mtext("Bilirubin", side = 4, line = 1)  
  
#second row: asat
 #circular model    
  plot(student_nocirc_noBili, 
       se     = FALSE, 
       #rug    = TRUE, 
       ylab   = "",
       xlab   = "",
       #yaxt   = "n",
       ylim   = c(-1,4), 
       xlim   = c(0, 550), 
       select = 1)
    abline(h=0, lty = 3)
    rug(unique(test_data$thrombo))
  
  plot(student_nocirc_all, 
       se     = FALSE, 
       #rug    = TRUE, 
       ylab   = "",
       xlab   = "",
       yaxt   = "n",
       ylim   = c(-1,4), 
       xlim   = c(0, 550), 
       select = 2)
    abline(h=0, lty = 3)
      rug(unique(test_data$thrombo))

  
 #circular model    
  plot(student_circ_noBili, 
       se     = FALSE, 
       #rug    = TRUE, 
       yaxt   = "n",
       ylab   = "",
       xlab   = "",
       ylim   = c(-1,4), 
       xlim   = c(0, 550), 
       select = 1)
    abline(h=0, lty = 3)
    rug(unique(test_data$thrombo))
  
  plot(student_circ_all, 
       se     = FALSE, 
       #rug    = TRUE, 
       ylab   = "",
       xlab   = "",
       yaxt   = "n",
       ylim   = c(-1,4), 
       xlim   = c(0, 550), 
       select = 2)
    abline(h=0, lty = 3)
      rug(unique(test_data$thrombo))
  mtext("ASAT", side = 4, line = 1)
    
  
#third row: hzv
#non-circular model
  plot(student_nocirc_noBili, 
       se     = FALSE, 
       #rug    = TRUE, 
       ylab   = "",
       xlab   = "",
       #yaxt   = "n",
       ylim   = c(-1,4),
       xlim   = c(0, 18),
       select = 2)
    abline(h=0, lty = 3)
    rug(unique(test_data$hzv))
  
  plot(student_nocirc_all, 
       se     = FALSE, 
       #rug    = TRUE, 
       ylab   = "",
       xlab   = "",
       yaxt   = "n",
       ylim   = c(-1,4),
       xlim   = c(0, 18),
       select = 3)
    abline(h=0, lty = 3)
    rug(unique(test_data$hzv))

  
 #circular model
  plot(student_circ_noBili, 
       se     = FALSE, 
       #rug    = TRUE, 
       yaxt   = "n",
       ylab   = "",
       xlab   = "",
       ylim   = c(-1,4),
       xlim   = c(0, 18),
       select = 2)
    abline(h=0, lty = )
    rug(unique(test_data$hzv))
  
  plot(student_circ_all, 
       se     = FALSE, 
       #rug    = TRUE, 
       ylab   = "",
       xlab   = "",
       yaxt   = "n",
       ylim   = c(-1,4),
       xlim   = c(0, 18),
       select = 3)
    abline(h=0, lty = 3)
    rug(unique(test_data$hzv))
  mtext("Cardiac Output", side = 4, line = 1)
  
#forth row: alat
  #non-circular model
  plot(student_nocirc_noBili, 
       se     = FALSE, 
       #rug    = TRUE, 
       ylab   = "", 
       xlab   = "",
       #yaxt   = "n",
       ylim   = c(-1,4), 
       xlim   = c(0, 7000), 
       select = 3)
    rug(unique(test_data$svri))
    abline(h=0, lty = 3)
  
  plot(student_nocirc_all, 
       se     = FALSE, 
       #rug    = TRUE, 
       ylab   = "", 
       xlab   = "",
       yaxt   = "n",
       ylim   = c(-1,4), 
       xlim   = c(0, 7000),
       select = 4)
    abline(h=0, lty = 3)
    rug(unique(test_data$svri))

  
  
   #circular model
  plot(student_circ_noBili, 
       se     = FALSE, 
       #rug    = TRUE,
       yaxt   = "n",
       ylab   = "", 
       xlab   = "",
       ylim   = c(-1,4), 
       xlim   = c(0, 7000), 
       select = 3)
    rug(unique(test_data$svri))
    abline(h=0, lty = 3)
  
  plot(student_circ_all, 
       se     = FALSE, 
       #rug    = TRUE, 
       ylab   = "", 
       xlab   = "",
       yaxt   = "n",
       ylim   = c(-1,4), 
       xlim   = c(0, 7000),
       select = 4)
    abline(h=0, lty = 3)
    rug(unique(test_data$svri))
  mtext("ALAT", side = 4, line = 1)
  
  
#fifth row: lactat
  #circular model
  plot(student_nocirc_noBili, 
       se     = FALSE, 
       #rug    = TRUE, 
       ylab   = "",
       xlab   = "",
       #yaxt   = "n",
       ylim   = c(-1,4),
       #xlim   = c(, ),
       select = 4)
    abline(h=0, lty = 3)
    rug(unique(test_data$urine24))
  
  plot(student_nocirc_all, 
       se     = FALSE, 
       #rug    = TRUE, 
       ylab   = "",
       xlab   = "",
       yaxt   = "n",
       ylim   = c(-1,4),
       #xlim   = c(, ),
       select = 5)
    abline(h=0, lty = 3)
    rug(unique(test_data$urine24))
 
  #circular model
  plot(student_circ_noBili, 
       se     = FALSE, 
       #rug    = TRUE,
       yaxt   = "n",
       ylab   = "",
       xlab   = "",
       ylim   = c(-1,4),
       #xlim   = c(, ),
       select = 4)
    abline(h=0, lty = 3)
    rug(unique(test_data$urine24))
  
  plot(student_circ_all, 
       se     = FALSE, 
       #rug    = TRUE, 
       ylab   = "",
       xlab   = "",
       yaxt   = "n",
       ylim   = c(-1,4),
       #xlim   = c(, ),
       select = 5)
    abline(h=0, lty = 3)
    rug(unique(test_data$urine24))
  mtext("Lactate", side = 4, line = 1)
  
  
par(mfrow = c(1,1), mar = c(5,4,4,2))
```




\newpage
## ABLATION STUDY I (REMOVE CIRCULAR FEATURE)
```{r ablation data set, include=FALSE}
ablation_data <- readRDS("ablation_set_with_sofa_predictions.rds")
```


### CIRCULAR MODEL
```{r accuracy measures on train se for circular teacher, echo=FALSE}
with(ablation_data, accuracy(target, sofa_circ))
with(ablation_data, class_accuracy(target, sofa_circ))
```

Confusion Matrix:
```{r, echo=FALSE}
xtabs(~ target + sofa_circ, data = ablation_data)
```



<!-- ### NON-CIRCULAR MODEL -->
```{r accuracy measures on train set for non-circular model, echo=FALSE, eval=FALSE}
with(ablation_data, accuracy(target, sofa_nocirc))
with(ablation_data, class_accuracy(target, sofa_nocirc))
```

<!-- Confusion Matrix: -->
```{r, echo=FALSE, eval=FALSE}
xtabs(~ target + sofa_nocirc, data = ablation_data)
```






\newpage
## SEARCH: Circular Teacher

```{r feature list for search based on corr with circular teacher, include=FALSE}
feature_list <- 
  corr_matrix[order(abs(corr_matrix[,"DNN w bili"]), decreasing=TRUE),][1:5,] %>%
  rownames(.) %>% 
  paste0("s(", .,")")

feature_list[1] <- "s(bili, k = 100)"
```

```{r liver_model_search for circular teacher, cache=TRUE, echo=FALSE, include=FALSE}
fitted_models <-
  #generate the power set of feature_list, and remove the void set 
  powerSet(feature_list)[-(2^length(feature_list))] %>%
  #build the symbolic model description  
  sapply(., function(...) glue("sofa_circ~{glue_collapse(..., sep='+')}")) %>%
  #fit the models to data, and extract key statistics
  tibble(formula_str = .,
         models      = lapply(X = .,
                              FUN  = function(m_str,...) bam(as.formula(m_str), ...),
                              data = test_data),
         data_fit    = floor(sapply(models, function(m) summary(m)$dev.expl) * 100),
         complexity  = sapply(models, function(...) attr(logLik(...), 'df'))) %>%
  #Sort the models so that we can find models that replicate the data well.
  #For this models data_fit should be approximately 100.
  arrange(desc(data_fit), complexity)
```


### TOP TEN 
```{r hit list for circular teacher, echo=FALSE}
fitted_models[,-2] %>% mutate(complexity = num(complexity, digits=2)) %>% slice(1:5)
```


<!-- ### SELECTED MODEL -->
```{r tuned candidate for circular teacher, echo=FALSE, eval=FALSE, include=FALSE}
selected_model <- gam(sofa_circ ~ s(bili, k = 100), data=test_data)

summary(selected_model)
```


\newpage
## SEARCH: Non-Circular Teacher

```{r feature list for search based on corr with non-circular teacher, include=FALSE}
feature_list <- 
  corr_matrix[order(abs(corr_matrix[,"DNN wo bili"]), decreasing=TRUE),][1:5,] %>%
  rownames(.) %>% 
  paste0("s(", .,")")
```

```{r liver_model_search for non-circular teacher, cache=TRUE, echo=FALSE, include=FALSE}
fitted_models <-
  #generate the power set of feature_list, and remove the void set 
  powerSet(feature_list)[-(2^length(feature_list))] %>%
  #build the symbolic model description  
  sapply(., function(...) glue("sofa_nocirc~{glue_collapse(..., sep='+')}")) %>%
  #fit the models to data, and extract key statistics
  tibble(formula_str = .,
         models      = lapply(X = .,
                              FUN  = function(m_str,...) bam(as.formula(m_str), ...),
                              data = test_data),
         data_fit    = floor(sapply(models, function(m) summary(m)$dev.expl) * 100),
         complexity  = sapply(models, function(...) attr(logLik(...), 'df'))) %>%
  #Sort the models so that we can find models that replicate the data well.
  #For this models data_fit should be approximately 100.
  arrange(desc(data_fit), complexity)
```


### TOP TEN 
```{r hit list for non-cirular teacher, echo=FALSE}
fitted_models[,-2] %>% mutate(complexity = num(complexity, digits=2)) %>% slice(1:5)
```


<!-- ### SELECTED MODEL -->
```{r tuned candidate for non-circular teacher, echo=FALSE, eval=FALSE, include=FALSE}
selected_model <- gam(sofa_nocirc ~ s(bili, k = 100), data=test_data)

summary(selected_model)
```


```{r liver_distill_fig3, echo=FALSE, fig.align="center", fig.height=4.5, fig.width=4.5, warning=FALSE, include=FALSE, eval=FALSE}
jump_bili <- function(x) (x > 12) + (x > 6) + (x > 2) + (x > 1.2) + 0

plot(selected_model, 
     se    = FALSE, 
     #rug   = TRUE, 
     xlim  = c(0,15), 
     ylim  = c(0,4),
     main = "",
     ylab  = "feature shape", 
     xlab = "bilirubin",
     shift = coef(selected_model)[1])
rug(unique(test_data$bili))
curve(jump_bili, from = 0, to = 15, n = 1001, add = TRUE, col = "blue", lty="dashed")
abline(v = c(1.2, 2, 6, 12), col = "blue", lty="dotted")
curve(jump_bili, from = 0, to = 15, n = 1001, add = TRUE, col = "blue", lty="dashed")
abline(v = c(1.2, 2, 6, 12), col = "blue", lty="dotted")
legend(legend = c("Theoretical", "Estimated"), 
       col    = c("blue", "black"),
       lty    = c("dashed", "solid"),
       bty    = "o",
       bg     = "white",
       x      = "topleft")
```